%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\documentclass{beamer}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{lipsum}
\apptocmd{\frame}{}{\justifying}{}

\usepackage[super]{nth}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\hoffset}{-0.25in}

\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
%\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedleft\large\justifying
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}\raggedright\raggedleft}
    \par
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth\raggedright}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rajathj//}{\Large Rajath John Bosco}} & Email : \href{mailto:rajathj2@illinois.edu}{rajathj2@illinois.edu}\\
  \href{https://www.linkedin.com/in/rajathj/}{https://www.linkedin.com/in/rajathj/} & Mobile : +1-217-819-9805 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Champaign, IL}
      {Master of Science in Information Management (Data Science Track)  }{Aug. 2019 -- Expected May 2021}
    \resumeSubheading
      {Sri Jayachamarajendra College of Engineering}{Mysore, India}
      {Bachelor of Engineering in Computer Science and Engineering;  GPA: 3.4 (8.5/10.0)}{Aug. 2012 -- July. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
 \resumeSubheading
 {Gies College of Business , UIUC}{Champaign , IL}
 {Course Assistant}{October 2019 - Present}
\resumeItemListStart
\resumeItem {iMBA}
 {Manage \& provide feedback to a class of 200+ students enrolled under iMBA courses using Asana \& Zoom.}
 \resumeItemListEnd
 
 \resumeSubheading
      {Visa Inc}{Bangalore, India}
      {Systems Analyst, Product Reliability Engineering}{July 2016 - Aug 2019}
      \resumeItemListStart
      
        \resumeItem {Visa AI Platform }{Developed scripts in Python and Shell to perform overall system health-check,check connectivity,  certificates and worked on CI/CD pipeline using Jenkins.
        Increased productivity by 50\% by deploying Python scripts to oversee the purging of log files containing 3+ Million transactions in HDFS.} 
        
        \resumeItem{Verified By Visa }{Developed complex SQL queries to analyze 20+ million transactions to identify sales patterns, anomalies and used Python to generate reports to monitor performance in realtime. }
        \resumeItem{Tokenization (Apple Pay, Android Pay etc.)} {Reduced 75\% of the overall time involved in the remediation of the servers by deploying python scripts to start and stop Mobile Wallet Gateway servers.}
        \resumeItem{Payments Systems Risk}{Boosted efficiency by 25\% by developing a smoke test framework in Python and integrated with Cloudview to automate server remediations. 
        }
        \resumeItem{Splunk} {
Queried machine-generated Big Data  to extract key metrics, devised alert mechanisms and visualised transaction data to  derive key insights to drive business efficiency
        }
        \resumeItem{Hackathon - Merchant Locator Chatbot (\nth{2} prize )}{Finished 2nd among 125 Teams by building a chatbot to call Visa's Merchant Locator API \& retrieve merchant data  to help people in distress find nearest available merchants.}
        \resumeItem{Achievements}  {Received 19 "Go Beyond" - Corporate recognition for achieving crucial  milestones. Promoted from Associate System Analyst to Systems Analyst on Dec 2018.}
        
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Tropical Storms}
 {Applied spatial trigonometry, line-intersection algorithms to find possible loops in the storms and used PyGeodesy to calculate speed, distance, etc. and categorized Atlantic and Pacific hurricanes from US NHC Data.
}

 \resumeSubItem{High-Tech Sculptures}
 {
Computed the stability of huge marble blocks when projected upon a particular shape using Convex Hull based on center of gravity and density.  Demonstrated Test-Driven Development in Python and continuous integration with the help of Travis CI.}
    \resumeSubItem{Product Analysis in Social Media}
    {
Achieved 82\% accuracy through sentiment analysis by using NLTK on product reviews obtained through Social Media using cron jobs and integrated it with a platform to visualize product specifications}
    \resumeSubItem{Credit Card Fraud Detection}
      {Achieved 86\% accuracy while classifying credit card frauds with the help of Sampling and logistic regression on an imbalanced Data-set.}

      
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
   {             Python, Java, SQL, C++, R, HTML, CSS, Javascript} 
      \resumeSubItem{Technologies}
      {          Docker, Soap UI, Jenkins, Jira, Splunk, GIT, REST }
     \resumeSubItem {Familiar}{Redis, TensorFlow, Hadoop, Hbase, Spark, Kafka, Hive, AWS, MongoDb}
     \resumeSubItem{Relevant Coursework}{ Data Structures, Software Engineering, Design and Analysis of Algorithms, Computer Networks, Data and Statistical Modelling, Programming Analytics, Machine Learning (Coursera).
 \resumeSubHeadingListEnd

%-------------------------------------------
\section{Activities}
 \resumeSubHeadingListStart
   \resumeSubItem{Linux Campus Club SJCE}
   {Conducted Sessions on Python , GIT , Machine Learning and worked on installing Ubuntu OS, Open Source Software on all the laboratory Systems.} 
   \resumeSubItem{Student Council SJCE}
   {Communicated and gave presentations to potential sponsors for the annual fest Jayciana, which helped in garnering funds of 15,000\$.}
     
     }
 \resumeSubHeadingListEnd



\end{document}
